A Recurrence

### 2014-11-26 draft.tex
Added period 6 to section 2

>>>>

We can also perform this analysis for period $6$  
\begin{proposition}
If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 6 and $f$ is a polynomial then $f(y) = cy$. 
\end{proposition}
\begin{proof} 
It is simple to see that $f(y)=cy$ produces a recurrence of period 6. Now we would like to show that all polynomial $f$ must be of this form. If we consider some arbitrary $f$ we know that we must have 
\begin{align*}
a_6 =x = \frac{f(a_5)}{a_4} \\ 
a_7 = y = \frac{f(a_6)}{a_5},
\end{align*}
and so $a_5 = \frac{f(x)}{y}$. This also gives us that 
\begin{equation*}
a_4 x = f\left( \frac{f(x)}{y} \right).
\end{equation*}
Noting that 
\begin{equation*}
a_4 = \frac{ x f(f(f(y)/x)/y)}{f(y)}, 
\end{equation*}
we obtain 
\begin{equation}
\label{period6}
 f\left( \frac{f(x)}{y} \right) = \frac{ x^2 f(f(f(y)/x)/y)}{f(y)}.
\end{equation}
Since $x$ and $y$ can take any values, we can set $y=1$ and let $x$ be arbitrary. Furthermore since $f$ is some polynomial it takes the form $f(z) = b_n z^n + \cdots + b_1 z +b_0$. Plugging these two into Equation \ref{period6} gives us 
\begin{equation*}
f(b_n x^n + \cdots + b_1 x + b_0) = x^2 f\left( b_n \frac{f(1)^n}{x^n} + \cdots + b_1 \frac{f(1)}{x} + b_0 \right).
\end{equation*}
We note that the largest exponent of $x$ on the left hand side is $n^n$ while the largest exponent of $y$ on the right hand side is $x^2$ if $b_0 \neq 0$. Since we can make $x$ arbitrarily large so that the term with the largest exponent dominates, this gives us that we must have $n^n=2$ if $b \neq 0$. This equation has no integer solutions and so we must have $b_0 =0$. Now if $b_1 \neq 0$ the largest exponent on the right hand side is $1$ and $n^n=1$ is solved by $n=1$ and so $f(z) = b_1 z$ as desired. 
\end{proof}
